fsOGTT Pre- and Post-ETI

### 2025-11-20 Christine Chan/EnVision CF/fsOGTT_pre_post_ETI.qmd
matsuda in table 1

```{r data cleaning}
# Import cleaned data
load("./Data_Clean/fsOGTT_pre_post_ETI.RData")
# Subset to people with more than one pre-ETI fsOGTT
multi_pre_df = df |>
  group_by(study_id) |>
  mutate(
    n_pre = sum(pre_post == "Pre"),
    time_diff_first_last = as.numeric(difftime(
      last(Date),
      first(Date),
      units = "days"
    ))
  ) |>
  filter(n_pre > 1)
var_label(multi_pre_df$n_pre) = "Number of fsOGTT pre-ETI"
var_label(multi_pre_df$time_diff_first_last) = "Days From First to Last fsOGTT"
# Save for Christine and Monique
write.csv(
  multi_pre_df,
  file = "./Data_Clean/fsOGTT_pre_post_ETI.csv",
  row.names = F,
  na = ""
)
```

@@

```{r}
#| label: tbl-1
multi_pre_df |>
  group_by(study_id) |>
  filter(row_number() == 1) |>
  ungroup() |>
  select(
    n_pre,
    time_diff_first_last,
    sex,
    age_visit,
    bmi,
    bmi_adult,
    bmi_perc,
    fev1,
    CFTR,
    pancreatic_status,
    Diagnosis,
    Insulin_0,
    Glucose_0,
    igi,
    iAUC30ins_over_gluc,
    iAUC120ins_over_gluc,
    iAUC180ins_over_gluc,
    odi_igi,
    odi_iauc
  ) |>
  tbl_summary(type = c("Insulin_0") ~ "continuous")
```

>>>>

```{r data cleaning}
setwd(home_dir)
# Import cleaned data
load("./Data_Clean/fsOGTT_pre_post_ETI.RData")
# Subset to people with more than one pre-ETI fsOGTT
multi_pre_df = df |>
  group_by(study_id) |>
  mutate(
    n_pre = sum(pre_post == "Pre"),
    time_diff_first_last = as.numeric(difftime(
      last(Date),
      first(Date),
      units = "days"
    ))
  ) |>
  filter(n_pre > 1)
var_label(multi_pre_df$n_pre) = "Number of fsOGTT pre-ETI"
var_label(multi_pre_df$time_diff_first_last) = "Days From First to Last fsOGTT"
# Save for Christine and Monique
write.csv(
  multi_pre_df,
  file = "./Data_Clean/fsOGTT_pre_post_ETI.csv",
  row.names = F,
  na = ""
)
```

@@

```{r}
#| label: tbl-1
multi_pre_df |>
  group_by(study_id) |>
  filter(row_number() == 1) |>
  ungroup() |>
  select(
    n_pre,
    time_diff_first_last,
    sex,
    age_visit,
    bmi,
    bmi_adult,
    bmi_perc,
    fev1,
    CFTR,
    pancreatic_status,
    Diagnosis,
    Insulin_0,
    Glucose_0,
    igi,
    iAUC30ins_over_gluc,
    iAUC120ins_over_gluc,
    iAUC180ins_over_gluc,
    odi_igi,
    odi_iauc,
    matsuda
  ) |>
  tbl_summary(type = c("Insulin_0") ~ "continuous")
```
